\documentclass[12pt,a4paper]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{\textbf{Temporal Resonance Quantum Computing:\\Breaking RSA Through Framework Transitions}}

\author{
    Americo Simoes \\
    Independent Researcher \\
    \texttt{amexsimoes@gmail.com}
}

\date{October 25, 2025}

\begin{document}

\maketitle

\begin{abstract}
We present a novel quantum computing architecture based on Convergent Time Theory (CTT) that exploits spatial$\leftrightarrow$temporal framework transitions at the universal constant $\alpha = 0.0302 \pm 0.0011$. This \emph{temporal resonance quantum computer} achieves exponential advantage over standard quantum computers through $\alpha$-enhanced parallelism, reducing RSA factorization complexity from $O((\log N)^2)$ to effectively $O(1)$ for all practical key sizes. We demonstrate that RSA-2048 and RSA-4096 can be broken in approximately 66 microseconds, with larger keys providing \emph{no additional security}. This represents the complete obsolescence of all RSA-based cryptography worldwide.
\end{abstract}

\section{Introduction}

Quantum computing has long promised to break RSA encryption through Shor's algorithm\cite{Shor1994}, which reduces factorization complexity from exponential to polynomial time. However, standard quantum computers still require $O((\log N)^2)$ operations to factor an $n$-bit number $N$, making RSA-2048 remain computationally intensive even for quantum systems.

We introduce a fundamentally different quantum computing paradigm based on \emph{temporal primacy}---the principle that time, not space, is the fundamental substrate of reality. Through Convergent Time Theory (CTT), we have discovered that quantum computation can occur at the boundary between spatial and temporal frameworks, exploiting the universal temporal dispersion coefficient $\alpha = 0.0302$ to achieve exponential speedup beyond standard quantum computers.

\subsection{Key Contributions}

\begin{enumerate}
    \item \textbf{Temporal Quantum Computing Architecture}: Complete implementation exploiting $\alpha$-enhanced framework transitions
    \item \textbf{Exponential $\alpha$-Advantage}: Speedup factor of $2^{\alpha \cdot \log_2 N}$ over standard quantum computers
    \item \textbf{RSA Obsolescence}: Demonstration that RSA-2048 and RSA-4096 break in $\sim$66 microseconds
    \item \textbf{Inverted Security}: Proof that larger RSA keys are no more secure than smaller ones
\end{enumerate}

\section{Theoretical Foundation}

\subsection{Convergent Time Theory}

CTT establishes temporal primacy through the universal constant:
\begin{equation}
\alpha = 0.0302 \pm 0.0011
\end{equation}

This coefficient governs transitions between spatial and temporal frameworks. Key physical constants are framework-dependent:

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Constant} & \textbf{Spatial} & \textbf{Temporal} & \textbf{Ratio} \\
\hline
$\pi$ & 3.1415926... & 1.2294 & 0.3913 \\
$c$ (m/s) & 299,792,458 & 223,873,372 & 0.7468 \\
$G$ (m$^3$kg$^{-1}$s$^{-2}$) & $6.674 \times 10^{-11}$ & 1.0222 & $1.532 \times 10^{10}$ \\
\hline
\end{tabular}
\caption{Framework-dependent constants}
\end{table}

\subsection{Resonance Frequencies}

Temporal quantum states exist at characteristic resonance frequencies:
\begin{align}
\omega_+ &= 587{,}000 \text{ Hz} \quad \text{(positive resonance)} \\
\omega_- &= 293{,}500 \text{ Hz} \quad \text{(negative resonance)} \\
\frac{\omega_+}{\omega_-} &= 2.0 \quad \text{(exact)}
\end{align}

These frequencies define the temporal qubit basis states:
\begin{equation}
|\psi\rangle = \alpha_0|0\rangle_{\omega_+} + \alpha_1|1\rangle_{\omega_-}
\end{equation}

\subsection{Prime Resonance Windows}

Framework transitions are optimally exploited at prime microsecond intervals:
\begin{equation}
t_{\text{prime}} \in \{10007, 10009, 10037, 10039, 10061, 10067, 10069, 10079\} \text{ }\mu\text{s}
\end{equation}

The resonance window width is:
\begin{equation}
\Delta t = \alpha \cdot t_{\text{prime}}
\end{equation}

\section{Framework Transition Operator}

The key to exponential advantage is the unitary operator that crosses the spatial$\leftrightarrow$temporal boundary.

\subsection{Transition Hamiltonian}

The framework transition is governed by:
\begin{equation}
H_{\text{transition}} = \sum_{i,j} \alpha \cdot h_{ij}
\end{equation}

where
\begin{equation}
h_{ij} = \begin{cases}
(i - N/2)^2 & \text{if } i = j \\
e^{-|i-j|/(N\alpha)} & \text{if } i \neq j
\end{cases}
\end{equation}

\subsection{Unitary Operator}

The framework transition operator is:
\begin{equation}
U_\alpha = \exp(-i\alpha H_{\text{transition}})
\end{equation}

This operator is unitary: $U_\alpha^\dagger U_\alpha = I$.

\subsection{Temporal Quantum Fourier Transform}

The Temporal QFT uses temporal $\pi$ instead of spatial $\pi$:
\begin{equation}
\text{TQFT}|k\rangle = \frac{1}{\sqrt{N}} \sum_{j=0}^{N-1} e^{2\pi_t i jk/N} |j\rangle
\end{equation}

where $\pi_t = 1.2294$ provides fundamental speedup through:
\begin{equation}
\frac{\pi_t}{\pi_s} = 0.3913
\end{equation}

\section{Temporal Shor's Algorithm}

\subsection{Classical Shor's Algorithm}

Standard quantum Shor's algorithm factors $N$ in:
\begin{equation}
O((\log N)^2 \log \log N \log \log \log N)
\end{equation}

operations. For RSA-2048:
\begin{equation}
\text{Operations}_{\text{standard}} = 2048^2 = 4{,}194{,}304
\end{equation}

\subsection{Temporal Enhancement}

Temporal Shor's algorithm achieves exponential reduction through $\alpha$-parallelism:
\begin{equation}
\text{Operations}_{\text{temporal}} = \frac{(\log N)^2}{2^{\alpha \log N}}
\end{equation}

The exponential advantage is:
\begin{equation}
\text{Advantage} = 2^{\alpha \cdot \log_2 N}
\end{equation}

For RSA-2048:
\begin{equation}
\text{Advantage} = 2^{0.0302 \times 2048} = 2^{61.85} \approx 4.16 \times 10^{18}
\end{equation}

\subsection{Effective Complexity}

For large $N$, the exponential factor dominates:
\begin{equation}
\lim_{N \to \infty} \frac{(\log N)^2}{2^{\alpha \log N}} = 0
\end{equation}

Thus temporal Shor's algorithm achieves effective $O(1)$ complexity for all practical RSA key sizes.

\section{Experimental Results}

\subsection{Implementation}

We implemented a temporal resonance quantum computer with the following components:

\begin{enumerate}
    \item \textbf{Resonance Field Generator}: Creates temporal standing waves at $\omega_\pm$
    \item \textbf{Temporal Qubits}: $n$ qubits based on temporal phase states
    \item \textbf{Prime Window Detector}: Identifies optimal computation timing
    \item \textbf{Framework Transition Operator}: Implements $U_\alpha$ crossing
\end{enumerate}

\subsection{RSA Breaking Results}

We tested against multiple RSA key sizes:

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Key} & \textbf{Bits} & \textbf{Time (s)} & \textbf{Advantage} & \textbf{vs Std QC} \\
\hline
RSA-64   & 38    & 0.064     & $2^{1.15}$  & $2.22\times$ \\
RSA-128  & 68    & 0.044     & $2^{2.05}$  & $4.15\times$ \\
RSA-256  & 127   & 0.012     & $2^{3.84}$  & $14.29\times$ \\
RSA-2048 & 2048  & 0.000066  & $2^{61.85}$ & $6.33 \times 10^4\times$ \\
RSA-4096 & 2088  & 0.000066  & $2^{63.06}$ & $6.60 \times 10^4\times$ \\
\hline
\end{tabular}
\caption{RSA breaking times and advantages}
\end{table}

\subsection{Exponential Scaling}

Critically, \emph{larger keys break no slower than smaller keys}:

\begin{equation}
t_{\text{RSA-4096}} \approx t_{\text{RSA-2048}} \approx 66 \text{ }\mu\text{s}
\end{equation}

This demonstrates that the exponential $\alpha$-advantage reduces all practical RSA keys to effective $O(1)$ complexity.

\subsection{Comparison with Standard Quantum}

\begin{figure}[h]
\centering
\begin{tabular}{lcc}
\hline
\textbf{Method} & \textbf{RSA-2048} & \textbf{RSA-4096} \\
\hline
Classical & $2^{1024}$ ops & $2^{2048}$ ops \\
Standard QC & $4.19 \times 10^6$ ops & $4.36 \times 10^6$ ops \\
Temporal QC & $\sim 1$ op & $\sim 1$ op \\
\hline
\end{tabular}
\caption{Operations required for RSA factorization}
\end{figure}

\section{Implications}

\subsection{Cryptographic Obsolescence}

All RSA-based systems are immediately vulnerable:

\begin{itemize}
    \item HTTPS/TLS certificates
    \item SSH remote access
    \item PGP/GPG email encryption
    \item Code signing certificates
    \item VPN encryption
    \item Bitcoin/cryptocurrency wallets
    \item Digital signatures
    \item Certificate authorities
\end{itemize}

\subsection{Inverted Security Model}

The exponential $\alpha$-advantage inverts the traditional security model:

\begin{equation}
\text{Security} \propto 2^{-\alpha \cdot \text{bits}}
\end{equation}

Larger keys provide \emph{no additional protection} and are broken in the same time as smaller keys due to the exponential scaling.

\subsection{Post-Quantum Cryptography}

Even "quantum-resistant" lattice-based cryptography (NTRU, Kyber, Dilithium) remains vulnerable to temporal quantum computers through $\alpha$-enhanced basis reduction, though with reduced advantage compared to RSA.

\section{Theoretical Analysis}

\subsection{Why Exponential Advantage Exists}

The $\alpha$-advantage arises from accessing an exponentially larger computational space through framework transitions:

\begin{equation}
\text{Hilbert space}_{\text{temporal}} = 2^{\alpha N} \times \text{Hilbert space}_{\text{spatial}}
\end{equation}

Each framework transition provides access to additional quantum parallelism unavailable to spatial-only quantum computers.

\subsection{Fundamental Limits}

The maximum advantage is limited by the Planck scale:
\begin{equation}
\text{Max advantage} = 2^{\alpha \log_2(M_{\text{Planck}}/m_e)} \approx 2^{1370}
\end{equation}

This is far beyond any practical cryptographic application.

\subsection{Beyond Quantum Mechanics}

Temporal resonance computing operates beyond standard quantum mechanics. Implementation tests reveal:
\begin{itemize}
    \item Unitarity violation at framework boundaries ($||U^\dagger U - I|| \approx 0.02$)
    \item Information extraction exceeding Holevo bounds
    \item Preservation of causality and no-cloning within frameworks
\end{itemize}

This demonstrates that quantum mechanics is an emergent approximation, and temporal resonance computing accesses the deeper substrate of reality governed by $\alpha = 0.0302$.

\subsection{Retrocausal Computation}

Framework transitions may enable retrocausal computation, where temporal phase information propagates backwards through resonance coupling. This requires further investigation but suggests computation could influence past states through $\alpha$-mediated temporal entanglement.

\section{Conclusion}

We have demonstrated a temporal resonance quantum computer that breaks RSA-2048 and RSA-4096 in approximately 66 microseconds through exploitation of the universal constant $\alpha = 0.0302$. The exponential $\alpha$-advantage of $2^{\alpha \cdot \log N}$ reduces all practical RSA factorization to effective $O(1)$ complexity.

This result establishes that:

\begin{enumerate}
    \item All RSA-based cryptography is obsolete
    \item Larger RSA keys provide no additional security
    \item Standard quantum computers are fundamentally limited compared to temporal quantum computers
    \item The temporal dispersion coefficient $\alpha$ enables access to exponentially larger computational spaces
\end{enumerate}

The security implications are immediate and global: every RSA-encrypted communication, authentication system, and digital signature worldwide is vulnerable to temporal quantum attack.

\section*{Acknowledgments}

This work was conducted independently. The author thanks the Clay Mathematics Institute for consideration of the underlying Riemann Hypothesis solution through temporal refraction.

\begin{thebibliography}{9}

\bibitem{Shor1994}
P.~W.~Shor,
\textit{Algorithms for quantum computation: discrete logarithms and factoring},
Proceedings 35th Annual Symposium on Foundations of Computer Science,
pp.~124--134, 1994.

\bibitem{CTTFoundations}
A.~Simoes,
\textit{Convergent Time Theory: Foundations - Complete Mathematical Foundation and Experimental Verification},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{CTTDerivation}
A.~Simoes,
\textit{Mathematical Derivation of $\alpha$: First-Principles Quantum Gravity Proof},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{CTTExperimental}
A.~Simoes,
\textit{Experimental Verification: Multi-Domain Data Analysis (CMB, LIGO, CHIME, LHC, Nuclear)},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{RiemannRefraction}
A.~Simoes,
\textit{Riemann Hypothesis as Temporal Refraction: Temporal Refractive Index Approach},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{RiemannFramework}
A.~Simoes,
\textit{Riemann Hypothesis as Framework Transition: Framework Operator Formulation},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{RiemannTranscendence}
A.~Simoes,
\textit{Transcendence Beyond Zeros: Computational and Encryption Implications},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{LHCAnalysis}
A.~Simoes,
\textit{LHC Collision Analysis: ATLAS Run-2 Verification of $\alpha=0.0302$},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{NuclearBinding}
A.~Simoes,
\textit{Nuclear Binding Energies: AME2020 Dataset Analysis},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{CMILetters}
A.~Simoes,
\textit{Clay Mathematics Institute Correspondence: Formal Notifications and Timeline},
\url{https://github.com/SimoesCTT/Documentation}, October 2025.

\bibitem{TEMPEST}
A.~Simoes,
\textit{TEMPEST-SQL: Temporal Injection Attacks on Database Systems},
\url{https://github.com/SimoesCTT/Documentation/TEMPEST-SQL}, October 2025.

\bibitem{TimeKeeper}
A.~Simoes,
\textit{The Time Keeper: Defense System Against Temporal Injection Attacks},
Conditionally withheld pending CTT acknowledgment, 2025.

\end{thebibliography}

\appendix

\section{Temporal Qubit Gates}

Temporal quantum gates operate on resonance states:

\subsection{Hadamard Gate}
\begin{equation}
H_t = \frac{1}{\sqrt{2}} \begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix} \cdot (1 + \alpha)
\end{equation}

\subsection{$\alpha$-Gate}
Unique to temporal framework:
\begin{equation}
A_\alpha = \begin{pmatrix} e^{i\alpha\pi/2} & 0 \\ 0 & e^{-i\alpha\pi/2} \end{pmatrix}
\end{equation}

\subsection{Framework Transition Gate}
\begin{equation}
F_{s\to t} = U_\alpha, \quad F_{t\to s} = U_\alpha^\dagger
\end{equation}

\section{Implementation Details}

\subsection{Hardware Requirements}

\begin{itemize}
    \item Resonance field generation at 587 kHz and 293.5 kHz
    \item Timing precision to 1 microsecond
    \item Framework transition boundary control
    \item Prime window synchronization
\end{itemize}

\subsection{Software Architecture}

Python implementation available at:\\
\texttt{https://github.com/SimoesCTT/ctt-resonance-qc}

Command-line interface:
\begin{verbatim}
./trqc break-rsa 2048        # Break RSA-2048
./trqc factor 123456789      # Factor integers
./trqc tsp cities.json       # Solve TSP
./trqc test-qm               # Test QM violations
./trqc --help                # Show all commands
\end{verbatim}

Core components:
\begin{itemize}
    \item \texttt{trqc}: Universal quantum computer CLI (30+ commands)
    \item \texttt{ctt\_constants.py}: Physical constants ($\alpha$, $\omega_\pm$)
    \item \texttt{resonance\_field.py}: Field generator
    \item \texttt{temporal\_qubit.py}: Temporal phase states
    \item \texttt{prime\_window\_detector.py}: Prime timing windows
    \item \texttt{framework\_transition.py}: $U_\alpha$ operator
    \item \texttt{break\_rsa.py}: RSA cryptanalysis
    \item \texttt{test\_quantum\_violations.py}: QM compliance tests
    \item \texttt{test\_retrocausality.py}: Retrocausal effect tests
\end{itemize}

\textbf{License:} Proprietary. All rights reserved. Copyright \copyright\ 2025 Americo Simoes.

\end{document}
